Software

### 2023-08-09 software.qmd
add stpphawkes R package

>>>>

## `stpphawkes`
I'm the lead author of the `stpphawkes` R package ([GitHub](https://github.com/sandialabs/stpphawkes)).

A R package for modeling of spatio-temporal and temporal point process using a Hawkes model accounting for missing data from the paper J. D. Tucker, L. Shand, and J. R. Lewis, "Handling Missing Data in Self-Exciting Point Process Models," Spatial Statistics, vol. 29. pp. 160-176, 2019. [PDF](Papers/SPATSTAT18_STPP.pdf)
